Borel regularity for exponential integrals and ODEs\\ [1ex]

### 2022-07-04 Introduction.tex
picture
Picture from PhD thesis of Niklas Zorbach: Computing Pat integrals with Lefschetz thimbles

where \textcolor{magenta}{ $\mathcal{C}_\alpha$ is a steepest descent path through the critical point $x_\alpha$ and $\theta$ is chosen such that $f(x_\beta)\notin f(x_\alpha)+[0,e^{i\theta}\infty)$ for $\beta\neq\alpha$}\footnote{Such a $\theta$ exists because $f$ has a finite number of critical points.}.
\color{magenta}
Let $\theta=0$, locally in a neighbourhood of a critcal point $x_\alpha$ we can choose a coordinate system $x_1,...,x_n$ such that $f(x)-f(x_\alpha)=x_1^2+...+x_n^2$. Then $\mathrm{Re}(f)$ is a Morse function with simple, isolated and non degenerate critical points. We choose a Riemannian metric $g$ on $X$ and we define the Lefschetz thimbles $\Gamma_{\alpha,z}$ as the steepstet descendet path issuing from a critcal point $x_\alpha$ (see \cite{pham}\cite{Witten}): denote $x'=\mathrm{Re}(x)$ and $x''=\mathrm{Im}(x)$, then 
\begin{equation}
\mathcal{C}_{\alpha,z}\defeq\lbrace x\in X\vert x_1''=x_2''=...=x_n''=0, x_1'^2+...+x_n'^2\leq \zeta-\zeta_\alpha\rbrace
\end{equation}
\begin{figure}
\caption{Lefschetz thimbles}\label{Lefschetz_thimbles}
\end{figure}
In addition, they generate the relative homology for every critical values \textbf{Why?}. If $\theta\neq 0$ we consider $xe^{i\theta/2}$.

>>>>

where \textcolor{magenta}{ $\mathcal{C}_\alpha$ is a steepest descent path through the critical point $x_\alpha$ and $\theta$ is chosen such that $f(x_\beta)\notin f(x_\alpha)+[0,e^{i\theta}\infty)$ for $\beta\neq\alpha$}\footnote{Such a $\theta$ exists because $f$ has a finite number of critical points.}.
\color{magenta}
Let $\theta=0$, locally in a neighbourhood of a critcal point $x_\alpha$ we can choose a coordinate system $x_1,...,x_n$ such that $f(x)-f(x_\alpha)=x_1^2+...+x_n^2$. Then $\mathrm{Re}(f)$ is a Morse function with simple, isolated and non degenerate critical points. We choose a Riemannian metric $g$ on $X$ and we define the Lefschetz thimbles $\mathcal{C}_{\alpha,z}$ as the steepstet descendet path issuing from a critcal point $x_\alpha$ (see \cite{pham}\cite{Witten}): 
\begin{equation}
\mathcal{C}_{\alpha,z}=\lbrace x\in X\,\big\vert \, \lim_{t\to -\infty} x(t)=x_\alpha\rbrace
\end{equation}

denote $x'=\mathrm{Re}(x)$ and $x''=\mathrm{Im}(x)$, then 
\begin{equation}
\mathcal{C}_{\alpha,z}\defeq\lbrace x\in X\vert x_1''=x_2''=...=x_n''=0, x_1'^2+...+x_n'^2\leq \zeta-\zeta_\alpha\rbrace
\end{equation}
\begin{figure}
\caption{Lefschetz thimbles}\label{Lefschetz_thimbles}
\end{figure}
In addition, they generate the relative homology for every critical values \textbf{Why?}. If $\theta\neq 0$ we consider $xe^{i\theta/2}$.
